PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-07-22 qfenv_paper/qf_environment.tex
more qf section

%Section heading
\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their
surroundings, with a strong dependence of the quiescent fraction of
galaxies on their local environment (e.g. \citealt{hubble36a,
oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
\citealt{blanton09a}).  The strength of this dependence is itself a
strongly decreasing function of galaxy stellar mass; at the extreme,
the lowest masses ($<10^{9}$ $M_\odot$) galaxies are quenched only in
dense regions, and never in isolation (\citealt{geha12a}).  These
effects vary with redshift at least in the densest clusters, as
observed in the changing fraction of late-type spirals relative to the
field found in studies of the morphology-density relation
(\citealt{dressler84a, desai07a}).  Clearly understanding the
properties of galaxies in the present-day universe requires a careful
investigation of the role of environment, and how that role changes
over time.

@@

\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations using the quiescent fraction - the fraction of galaxies that have depleted their star-formation. With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments. More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution over redshift for galaxies in low and high density environments. Through this comparison we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed quenching mechanisms, such as strangulation and ram-pressure stripping (CITECITE), that operate on the scale of our environment measure.

@@

Most noticeably, $f_{\rm{Q}}$ increases monotonically as a function of mass regardless of redshift bin or environment. In other words, for all subsamples, galaxies in higher mass bins are more likely to have quenched its star-formation. With the roughly linear correlation between galaxy SFR to galaxy color and morphology, we find that this trend reflects the well established color-mass and morphology-mass relations: more massive galaxies are more likely to be red or early-type (\cite{Blanton:2009aa}).

Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments and over our mass range $f_{\rm{Q}}$ increases as redshift decreases. For high density environment, this is analogous to the Butcher-Omeler Effect (\cite{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift. For all environments a larger portion of our galaxy population has quenched its star-formation over time. Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results strongly support the observed decline of global star-formation in the universe (\cite{hopkins06a}).

Also, by comparing the stellar masses at which $f_{\rm{Q}} = 0.5$ for each subsample, we find that this mass decreases over cosmic time. This corresponds to the well-known mass-downsizing pattern (\cite{bundy06a}). Furthermore, the mass-downsizing trend observed in each of our environment subsample is generally consistent with the trend observed in zCOSMOS Redshift Survey for isolated and group galaxies (\cite{Iovino:2010aa}).

We compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}$ or $f_{\rm{red}}$ measurements for analogous environment classifications in literature. For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for SDSS galaxies as a function of environment. For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M}_{*} = [9.8, 10.1]$. The \cite{Tinker:2011aa} $f_{\rm{Q}}$ values at the lowest and highest overdensity values, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our SDSS sample low and high density environment $f_{\rm{Q}}$ at the lowest mass bin $\rm{log} \; \mathcal{M} \sim 10.2$. At higher mass ranges, our $f_{\rm{Q}}$ results for low and high density environments are consistent with \cite{Baldry:2006aa} $f_{\rm{red}}$ values for lowest and highest environment density, which they measure using projected neighbor density.

At higher redshifts, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which roughly covers the same redshift range as PRIMUS. \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and environment determined using a group catalog, 3D local density contrast, and overdensity respectively, compare $f_{\rm{red}}$ for different environments.

The $f_{\rm{blue}}$ values for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $f_{\rm{Q}}$ values in high and low density environments. Similarly, the $f_{\rm{red}}$ values for high and low overdensities from \cite{Kovac:2014aa} disagree with our $f_{\rm{Q}}$ values in high and low density environments.

Also, the zCOSMOS results, which are mostly consistent with each other, indicate that the $f_{\rm{red}}$ values in high density environments are greater than in low density environments. The same trend is observed in the PRIMUS results and will be discussed in detail later in the section. 
Furthermore, \cite{Iovino:2010aa} in their analysis finds clear mass dependence in the $f_{\rm{red}}$ evolution where $f_{\rm{red}}$ evolves by a greater amount for lower mass galaxies in both group and isolated galaxies.

 %explain the zCOSMOS results briefly. Mention the general discrepancies while highlighting the large statistics offered by PRIMUS
%If we impose the f_Q vs f_red discrepancies plotting in Kovac et al. 2014, can we explain the discrepancies between Iovino et al. 2010 and PRIMUS? Is Iovino et al. 2010 and Kovac et al. 2014 consistent with one another? 
%Note the clear mass dependence in essentially all the zCOSMOS results 
%color-density relation?

In contrast to the zCOSMOS results, for each panels in Figure \ref{fig:qf}, qualitatively, we see little mass dependence on the $f_{\rm{Q}}$ evolution. However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, we require a more quantitative comparison of the $f_{\rm{Q}}$ redshift evolution. Consequently, we fit each subsample $f_{\rm{Q}}$ to a power-law parameterization as a function of stellar mass,

@@

The same fitting was performed using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$; however, aside from a general shift in all $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ values by roughly $\sim 0.2$, we observe the same evolutionary trends.

@@

%PRIMUS results are roughly in agreement with zCOSMOS 10k (Iovino et al. 2010) and zCOMOS 20k (Kovac et al. 2014) once the difference between f_red and f_Q are taken into account. Discuss some general specific values. 
% Previous results, primarily from zCOSMOS 10k and 20k, have found a significant mass dependence in the f_{Q} evolution with f_{Q} increasing significantly more over redshift at lower masses. At higher masses these results find little evolution in f_Q. Though our f_{Q} values are in good agreement with these results, for the mass ranges probed in our analysis, we find little mass dependence in the f_Q evolution.

% color-mass relation, mass-density relation, color-density relation, SFR-density relation, SSFR-density relation,

% The "color-mass" relation holds for both low and high environment galaxies. While others in literature (Cucciati et al. 2010) found that the mass dependence was less apparent in high environment, this does not hold true for the SDSS and PRIMUS data. Although this could be due to the contamination in our environment measurements since there are large redshift errors. 
% Emphasize that due to the limited mass range from mass completeness limits, the conclusions on mass dependence should be taken with a grain of salt. 
% The redshift evolution of the QF in each

@@

1. SMFs in low and high environment are different for both SF and Q
2. Mass dependence of QF
3. redshift dependence of Qf
4. environment dependence of QF
5. QF fit

>>>>

%Section `ing
\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their
surroundings, with a strong dependence of the quiescent fraction of
galaxies on their local environment (e.g. \citealt{hubble36a,
oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
\citealt{blanton09a}).  The strength of this dependence is itself a
strongly decreasing function of galaxy stellar mass; at the extreme,
the lowest masses ($<10^{9}$ $M_\odot$) galaxies are quenched only in
dense regions, and never in isolation (\citealt{geha12a}).  These
effects vary with redshift at least in the densest clusters, as
observed in the changing fraction of late-type spirals relative to the
field found in studies of the morphology-density relation
(\citealt{dressler84a, desai07a}).  Clearly understanding the
properties of galaxies in the present-day universe requires a careful
investigation of the role of environment, and how that role changes
over time.

@@

\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating quiescent fraction - the fraction of galaxies that have depleted their star-formation. With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments. More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution over redshift for galaxies in low and high density environments. Through this comparison we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed quenching mechanisms, such as strangulation and ram-pressure stripping (CITECITE), that operate on the scale of our environment measure.

@@

Most noticeably, $f_{\rm{Q}}$ increases monotonically as a function of mass at all redshift bin and environment. In other words, for all subsamples, galaxies in higher mass bins are more likely to have quenched its star-formation. With the roughly linear correlation between galaxy SFR to galaxy color and morphology, we find that this trend reflects the well established color-mass and morphology-mass relations: more massive galaxies are more likely to be red or early-type (\cite{blanton09a}).

Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments and over our mass range $f_{\rm{Q}}$ increases as redshift decreases. For high density environment, this is analogous to the Butcher-Omeler Effect (\cite{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift. For all environments a larger portion of our galaxy population has quenched its star-formation over time. Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results strongly agree with the observed decline of global star-formation in the universe (\cite{hopkins06a}).

In addition, when we compare the stellar masses at which $f_{\rm{Q}} = 0.5$ for each subsample, we find that this mass decreases over cosmic time. This corresponds to the well-known mass-downsizing pattern in the literature (e.g. \cite{bundy06a}). Furthermore, the mass-downsizing trend observed in each of our environment subsample is consistent with the trend observed in zCOSMOS Redshift Survey for isolated and group galaxies (\cite{Iovino:2010aa}). %Remark on how the M_{50-50}? is lower for high environment f_{Q}, and that it generally increases with redshift. A trend also observed in the t_{5050} considerations.

Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for analogous environment classifications. For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for SDSS galaxies as a function of environment. For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M}_{*} = [9.8, 10.1]$. The \cite{Tinker:2011aa} $f_{\rm{Q}}$ values at the lowest and highest overdensity values, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our SDSS sample low and high density environment $f_{\rm{Q}}$ at the lowest mass bin $\rm{log} \; \mathcal{M} \sim 10.2$. At higher mass ranges, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}. \cite{Baldry:2006aa} using project neighbor density environment measures ($\rm{log} \;  \Sigma$) in order to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities. Although the different environment measurement makes a direct comparison unclear, $f_{\rm{Q}}$ for higher environments ($\rm{log} \; \Sigma > 0.2$) in \cite{Baldry:2006aa} is roughly $f_{\rm{Q}} \sim 0.6$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.9$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, in agreement our high density environment. Likewise, for lower environments in \cite{Baldry:2006aa} ($\rm{log} \; \Sigma < -0.4$) $f_{\rm{Q}} \sim 0.4$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.8$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, which agrees with our low density environment $f_{\rm{Q}}$.

For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which approximately covers the same redshift range as PRIMUS. \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment. The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments. Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments. However, \cite{Kovac:2014aa} illustrates that there is a significant difference between classifying the quenched population using color and SFR: $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by $\sim 0.2$. Although the difference does not propagate evenly for the environment classification, once we approximately account for the difference $f_{\rm{red}}$ in \cite{Kovac:2014aa} is generally consistent with our $f_{\rm{Q}}$ results for both high and low density environments. %Highlight that PRIMUS has more statistics?

Additionally, the zCOSMOS results indicate that the $f_{\rm{red}}$ values in high density environments are greater overall than in low density environments. The same trend is observed in the PRIMUS results and will be discussed in detail later in the section. Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution. \cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution for lower masses. In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over $0.4 \lesssim z \lesssim 0.9$. On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies. In contrast, in each panels in Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments. However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern. In order to more quantitatively compare the $f_{\rm{Q}}$ evolution, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass,

@@

Figure \ref{fig:qffit} illustrates that throughout the entire redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the lower density environment. This is in strong agreement with the zCOSMOS results from \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa}. Therefore, for $z < 1.0$, galaxy populations in higher density environments have higher quenched fractions.

The same fitting was performed using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$; however, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends. $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments increases by $\sim 0.2$ from as redshift decreases from $z \sim 0.7$ to $z \sim 0.1$. 
This suggests that the total amount of $f_{\rm{Q}}$ evolution at $\mathcal{M} \sim This further supports our previous suggestion that there is little mass dependence in our $f_{\rm{Q}}$ evolution. Although our sample from PRIMUS provides larger statistics, due to the limited mass ranges probed in our mass-complete sample ($\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin) it is difficult to dismiss the mass dependence observed in the zCOSMOS results.

@@

% The "color-mass" relation holds for both low and high environment galaxies. While others in literature (Cucciati et al. 2010) found that the mass dependence was less apparent in high environment, this does not hold true for the SDSS and PRIMUS data. Although this could be due to the contamination in our environment measurements since there are large redshift errors.

@@

\begin{itemize}
	\item 1. SMFs in low and high environment are different for both SF and Q
	\item 2. Mass dependence of QF
	\item 3. redshift dependence of Qf
	\item 4. environment dependence of QF
	\item 5. QF fit 
\end{itemize}
